Supplementary Materials

### 2019-01-30 sup_mat/sup_mat.Rmd
made changes to plots
RT plots show raw RT instead of log2(RT)

---
title: "Supplementary Materials"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    fig_caption: yes
fig_height: 4
fig_width: 6
---

@@

```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center"}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

@@

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```
### Foraging
No participants were excluded for poor performance on the foraging task. However, participant 27 and participants 40 to 43 were missing their data from the feature search condition (Figure \ref{fig:For_switch_rt}). We had not planned to use the results from the feature search condition in the correlation calculations, so these participants were not excluded.

```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Average repetition rate (i.e. when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
# again, what sort of plots are we interester in?

@@

plt_for_sr_rt <- plt_for_sr_rt %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, Search_cond, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, Search_cond) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = Search_cond)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom",
        strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt_for_sr_rt$labels$y <- "Response Time (secs)"
plt_for_sr_rt$labels$x <- "Average Repetition Rate"
plt_for_sr_rt$labels$colour <- "Search Condition"
plt_for_sr_rt

@@

```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Log2 transformed Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks. The plot for the Adaptive Choice task is split between RTs for optimal choices (i.e. picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre"}
# make rt plots 
# do SH first 
plt_sh_rt <- ls_acc_RT %>%
  mutate(log2rt = log2(rt)) %>%
  ggplot(aes(log2rt)) + 
  geom_histogram() + 
  theme_bw() + 
  facet_wrap(~targSide)
plt_sh_rt$labels$x <- "Log2 Response Time (msecs)"

plt_acs_logrt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice),
         sdev = sd(log2_RT),
         mean_rt = mean(log2_RT)) %>%
  filter(log2_RT > mean_rt - 3*sdev,
         log2_RT < mean_rt + 3*sdev,
         log2_RT > log2(300)) %>%  
  ggplot(aes(log2_RT,
             colour = Optimal_Choice,
             fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(legend.position = "bottom",
        strip.text.x = element_blank()) + 
  scale_colour_ptol() + 
  scale_fill_ptol() + 
  facet_wrap(~Optimal_Choice)
plt_acs_logrt$labels$x <- "Log2 Response Time (msecs)"

>>>>

---
title: "Supplementary Materials"
output:
  pdf_document:
    toc: yes
    toc_depth: 4
    fig_caption: yes
fig_height: 2
fig_width: 6
---

@@

```{r ls_acc_plt, fig.cap = "\\label{fig:ls_acc_plt} Accuracy data for each participant for the split-half paradigm. ", echo = FALSE, fig.align = "center", fig.asp = 0.6}
# make the plot
plt <- ls_acc_RT %>%
  group_by(observer, targSide, session) %>%
  summarise(Accuracy = mean(accuracy)) %>%
  ggplot(aes(targSide, Accuracy, fill = session)) + 
  geom_bar(stat = "identity", position = position_dodge()) + 
  scale_y_continuous(breaks = c(0,1)) + 
  theme_bw() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.5), legend.position = "top", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) + 
  scale_fill_ptol() +
  facet_wrap(~observer)
plt$labels$x <- "Target Condition"
plt
```

@@

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.asp = 0.6}
plt_ACS_mean_acc
```
### Foraging
No participants were excluded for poor performance on the foraging task. However, participant 27 and participants 40 to 43 were missing their data from the feature search condition (Figure \ref{fig:For_switch_rt}). We had not planned to use the results from the feature search condition in the correlation calculations, so these participants were not excluded.

```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Average repetition rate (i.e. when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center", fig.asp = 0.6}
# again, what sort of plots are we interester in?

@@

plt_for_sr_rt <- plt_for_sr_rt %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, Search_cond, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, Search_cond) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = Search_cond)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom",
        strip.text.x = element_text(margin = margin(0.008,0,0.008,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt_for_sr_rt$labels$y <- "Response Time (secs)"
plt_for_sr_rt$labels$x <- "Average Repetition Rate"
plt_for_sr_rt$labels$colour <- "Search Condition"
plt_for_sr_rt

@@

```{r ACS_SH_rt, fig.cap = "\\label{fig:ACS_SH_rt} Response time distributions for the Split-Half (top) and Adaptive Choice (bottom) tasks. The plot for the Adaptive Choice task is split between RTs for optimal choices (i.e. picking the colour in the minority as indicated by a 1) and the suboptimal choice", echo = F, warnings = F, message = F, fig.align = "centre", fig.asp = 0.6}
# make rt plots 
# do SH first 
plt_sh_rt <- ls_acc_RT %>%
  ggplot(aes(rt)) + 
  geom_histogram() + 
  theme_bw() + 
  facet_wrap(~targSide)
plt_sh_rt$labels$x <- "Response Time (msecs)"

plt_acs_logrt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice),
         sdev = sd(RT),
         mean_rt = mean(RT)) %>%
  filter(RT > mean_rt - 3*sdev,
         RT < mean_rt + 3*sdev,
         RT > 300) %>%  
  ggplot(aes(RT,
             colour = Optimal_Choice,
             fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(legend.position = "bottom",
        strip.text.x = element_blank()) + 
  scale_colour_ptol() + 
  scale_fill_ptol() + 
  facet_wrap(~Optimal_Choice)
plt_acs_logrt$labels$x <- "Response Time (msecs)"
